### 2011-11-22 doc/theses/vitasek/chapter-0-preface.tex
Thesis: fixing singletons and merging Kesy.

Along with technologies such as SQL/noSQL\footnote{noSQL: collection of non-relational database technologies, \url{http://nosql-database.org/}.} databases, proprietary binary file formats, plain-text configuration files and JSON\footnote{JSON: JavaScript Object Notation, lightweight data format, \url{http://www.json.org/}.}, XML is one of the leading formats for storing structured data. However, even though languages such as DTD and XML Schema\footnote{DTD and XML Schema: 2 most prominent XML schema languages, \cite{Bray:08:EML}} to describe XML structure exist for a long time, most of the documents use outdated or no schema at all \cite{1802522}. To tackle this problem one may employ reverse-engineering techniques to infer the schema from existing documents, such as those described in \cite{ahonen, bex, vyhnanovska}. In particular, \cite{archdoc} introduces the jInfer schema inference framework, dealing primarily with the structural parts of the schema: how all the elements, attributes and text data are to be organized in an XML document conforming to~that schema. Inference of this kind of structural information was greatly improved in \cite{anti}.\\

@@

Pseudocode examples such as the one in Listing \ref{listing-example} will always be presented in a functional way, with inputs and outputs of the function clearly marked in the beginning.

>>>>

Along with technologies such as SQL/noSQL\footnote{noSQL: collection of non-relational database technologies, \url{http://nosql-database.org/}.} databases, proprietary binary file formats, plain-text configuration files and JSON\footnote{JSON: JavaScript Object Notation, lightweight data format, \url{http://www.json.org/}.}, XML is one of the leading formats for storing structured data. However, even though languages such as~DTD and XML Schema\footnote{DTD and XML Schema: 2 most prominent XML schema languages, \cite{Bray:08:EML}} to describe XML structure exist for a long time, most of the documents use outdated or no schema at all \cite{1802522}. To tackle this problem one may employ reverse-engineering techniques to infer the schema from existing documents, such as those described in \cite{ahonen, bex, vyhnanovska}. In~particular, \cite{archdoc} introduces the jInfer schema inference framework, dealing primarily with the structural parts of the schema: how all the elements, attributes and text data are to be organized in an XML document conforming to~that schema. Inference of this kind of structural information was greatly improved in \cite{anti}.\\

@@

Pseudocode examples such as the one in Listing \ref{listing-example} will always be presented in a functional way, with inputs and outputs of the function clearly marked in~the~beginning.
